Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-11-18 grove-paper.tex
Remove references to no longer existing figures

We merge these edits by including \emph{both} edges as edges going out of the \texttt{R} position
of \vWrapPlus{}.
This results in \autoref{fig:MultiChild:c}.
The conflict between Alice's and Bob's changes is
represented by the fact that there are multiple edges going out of one index.
In the user interface, we flag this conflict with the notation~\texttt{\{ x | y \}}
as shown in \autoref{fig:MultiChild:d}.

@@

On their own, neither of these edits creates a cycle.
However, merging the edit actions of both Alice and Bob results in the graph
in \autoref{fig:Cycle:d}, which has a cycle
between~\vMultiCycleTimes{} and~\vMultiCyclePlus{}.
This situation is akin to a merge conflict in traditional version control systems.
Resolving it requires user input, but is as simple as
either deleting~\eMultiCycleBobPlus{} and~\eMultiCycleBobTimes{}~(thus favoring Alice's version)
or deleting~\eMultiCycleAliceTimes{} and~\eMultiCycleAlicePlus{}~(thus favoring Bob's version).
Since a cycle like this that is connected to the root vertex always
contains vertexes with multiple parents that if removed would break the cycle,
we use the user interface described in \autoref{sub:Multi-parent conflicts}
to display these kinds of programs.
For example, \autoref{fig:Cycle:d} would be displayed
as shown in \autoref{fig:Cycle:e}.
We leave the user interface considerations of resolving the conflict such a
cycle represents to future work.

>>>>

We merge these edits by including \emph{both} edges as edges going out of the \texttt{R} position
of \vWrapPlus{}.
This results in \autoref{fig:MultiChild:c}.
The conflict between Alice's and Bob's changes is
represented by the fact that there are multiple edges going out of one index.
In the user interface, we flag this conflict with the notation~\texttt{\{ x | y \}}.

@@

On their own, neither of these edits creates a cycle.
However, merging the edit actions of both Alice and Bob results in the graph
in \autoref{fig:Cycle:d}, which has a cycle
between~\vMultiCycleTimes{} and~\vMultiCyclePlus{}.
This situation is akin to a merge conflict in traditional version control systems.
Resolving it requires user input, but is as simple as
either deleting~\eMultiCycleBobPlus{} and~\eMultiCycleBobTimes{}~(thus favoring Alice's version)
or deleting~\eMultiCycleAliceTimes{} and~\eMultiCycleAlicePlus{}~(thus favoring Bob's version).
Since a cycle like this that is connected to the root vertex always
contains vertexes with multiple parents that if removed would break the cycle,
we use the user interface described in \autoref{sub:Multi-parent conflicts}
to display these kinds of programs.
For example, \autoref{fig:Cycle:d} would be displayed.
We leave the user interface considerations of resolving the conflict such a
cycle represents to future work.
